The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-08-29 paper/ms.tex
lpv section init
Revert "typo"
This reverts commit 431b81bedd3f5d8f3f3bb40cb8bcbcbffe43756f.

\subsubsection{Chemical Composition}
\label{chemical}
The chemical compositions for each star were measured in the $\alpha$ (Mg, Ti, Si, Ca), odd-Z (Al, Na, Cu, Sc, V), Fe-peak (Fe, Ni, Zn, Co, Cr, Mn), and neutron capture (Sr, Y, Zr, Ba, La, Nd, Eu) elemental families. This was done to asses the Galactic populations from which these stars are drawn. The first thing to note is that the metallicities, which are tabulated in Table~\ref{stellar_props}, are too high (with $-0.51<$~[M/H]~$<$ +0.14~dex) to be considered drawn from the Galactic halo, whose peak metallicity is around $\sim -1.50$ \cite[e.g.][]{Chiba2000}. Furthermore, the distance distribution, noted in Table~\ref{all_stars}, indicates that all stars are located within a few~kpc of the Sun and thus are not apart of the Galactic bulge. These alone allow us to predict that these stars are drawn from only the Galactic thick and thin disks. We provide a detailed chemical abundance analysis below to support this claim.\\
{\bf $\alpha$ elements:}\\
\begin{figure*}
\noindent\includegraphics[width=\textwidth,keepaspectratio]{Pope_spectra_alphaele.pdf}

@@

@@

This work was performed in part under contract with the Jet Propulsion Laboratory (JPL) funded by NASA through the Sagan Fellowship Program executed by the NASA Exoplanet Science Institute. B.P. also acknowledges support from Balliol College and the Clarendon Fund. D.H. acknowledges support by the Australian Research Council's Discovery Projects funding scheme (project number DE140101364) and support by the NASA Grant NNX14AB92G issued through the \emph{Kepler} Participating Scientist Program.

>>>>

\subsubsection{Chemical Composition}
\label{chemical}
The chemical compositions for each star were measured in the $\alpha$ (Mg, Ti, Si, Ca), odd-Z (Al, Na, Cu, Sc, V), Fe-peak (Fe, Ni, Zn, Co, Cr, Mn), and neutron capture (Sr, Y, Zr, Ba, La, Nd, Eu) elemental families. This was done to asses the Galactic populations from which these stars are drawn. The first thing to note is that the metallicities, which are tabulated in Table~\ref{stellar_props}, are too high (with $-0.51<$~[M/H]~$<$ +0.14~dex) to be considered drawn from the Galactic halo, whose peak metallicity is around $\sim -1.50$ \cite[e.g.][]{Chiba2000}. Furthermore, the distance distribution, noted in Table~\ref{all_stars}, indicates that all stars are located within a few~kpc of the Sun and thus are not apart of the Galactic bulge. These alone allow us to predict that theses stars are drawn from only the Galactic thick and thin disks. We provide a detailed chemical abundance analysis below to support this claim.\\
{\bf $\alpha$ elements:}\\
\begin{figure*}
\noindent\includegraphics[width=\textwidth,keepaspectratio]{Pope_spectra_alphaele.pdf}

@@

\subsubsection{Long Period Variables}
\label{lpvs}

@@

This work was performed in part under contract with the Jet Propulsion Laboratory (JPL) funded by NASA through the Sagan Fellowship Program executed by the NASA Exoplanet Science Institute. B.P. also acknowledges support from Balliol College and the Clarendon Fund. D.H. acknowledges support by the Australian Research Council's Discovery Projects funding scheme (project number DE140101364) and support by the NASA Grant NNX14AB92G issued through the \emph{Kepler} Participating Scientist Program. DWL acknowledges partial support from the Kepler Extended Mission under NASA Cooperative Agreement NNX13AB58A with the Smithsonian Astrophysical Observatory.
